Paper_analyses

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@

@@

@@

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_ground_valence)

@@

hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
                                        + (1 | ssid),
                                     # (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_ar_vl)

@@

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, Bio_Mean_HR))+
  geom_point()+
  # xlim()
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()
```

>>>>

table(is.na(db_full4new_stim_screen_pupil_nopract$Group))

table(db_full4new_stim_screen_pupil_nopract$Group)

 db_full4new_stim_screen_pupil_nopract %>%
   subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()
  facet_grid(~mediansplit_sample_arousal2)

@@

db_full4new_stim_screen_pupil_nopract$valence_abs<- abs(db_full4new_stim_screen_pupil_nopract$valence)
db_full4new_stim_screen_pupil_nopract$valence_abs_c<- scale(db_full4new_stim_screen_pupil_nopract$valence_abs, center = TRUE,scale = TRUE)[,1]

@@

# abs
pupil_arousal_findings$pupil_from_vale__tas_abs <- lmer(pup_basCor ~ valence_abs_c* TASc +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT"))

db_full4new_stim_screen_pupil_nopract$arousal_abs<- abs(db_full4new_stim_screen_pupil_nopract$arousal)
db_full4new_stim_screen_pupil_nopract$arousal_abs_c<- scale(db_full4new_stim_screen_pupil_nopract$arousal_abs, center = TRUE,scale = TRUE)[,1]

pupil_arousal_findings$pupil_from_ar__tas_abs <- lmer(pup_basCor ~ arousal_abs_c* TASc +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT"))

summary(pupil_arousal_findings$pupil_from_ar__tas_abs)

cor.test(db_full4new_stim_screen_pupil_nopract$valence_abs_c, abs(db_full4new_stim_screen_pupil_nopract$arousal))
```

@@

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor,color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence))+

 # stat_summary(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence), fun = mean,geom = "line", size = 1.5)
 #  
  # stat_smooth(aes(group= mediansplit_ground_arousal), fun = mean,geom = "line",
  #              se = F, alpha = 1, size = 1.5)+
  stat_smooth(size=1.5, method = "loess", level = 0.95, 
    fullrange = TRUE, se = FALSE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   labs(color  = "mediansplit_ground_arousal", linetype = "mediansplit_ground_valence")
   facet_grid(~mediansplit_ground_valence)

@@

hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
                                        + (1 | ssid)+
                                     (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_ar_vl)

db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif))%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(valence_c, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  xlim(-.4,.6)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif))%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(valence_c, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  xlim(-.4,.6)
  ggpubr::stat_cor()

@@

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, Bio_Mean_HR_dif))+
  geom_point()+
  # xlim()
  geom_smooth(method = lm, se = F)+
  # geom_smooth(aes(group = ssid),method = lm, se = F)
  ggpubr::stat_cor()

inter_bio<- lmer(pup_basCor~Bio_Mean_HR_dif +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
                 REML = FALSE,
                 data = db_full6new_hr_fix_stim_nt1.1)

summary(inter_bio)

inter_bio1<- lmer(Bio_Mean_HR_dif~ pup_basCor +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
                 REML = FALSE,
                 data = db_full6new_hr_fix_stim_nt1.1)

summary(inter_bio1)

inter_bio2<- lmer(log1p(BIO_CDA.PhasicMax+.1)~ Bio_Mean_HR_dif + pup_basCor + (1|ssid)+ 
                    (1|stimIAPS), 
                 REML = FALSE,
                 data = db_full6new_hr_fix_stim_nt1.1)

summary(inter_bio2)

# cluster based on bio, pupil angsr_selfrep_matrixthen take these clusters and compare arousal valence
```
